Presentation Materials

### 2017-03-13 San Antonio/presentation_materials.Rmd
updated markdown

---
title: "Presentation Materials"
author: "Yu"
date: "3/12/2017"
output: 
  html_document:
    toc: true
    theme: united
---

@@

#### [Sago Mine (4608791, clearly wrong)](https://en.wikipedia.org/wiki/Sago_Mine_disaster)

@@

>>>>

---
title: "Presentation Materials"
author: "Yu"
date: "3/13/2017"
output: 
  html_document:
    toc: true
    theme: united
---

@@

#### [No. 5 Mine (101322)](http://www.chicagotribune.com/news/chi-0209220285sep22-story.html)

Usable violation data only date back to 2000.

#### [Sago Mine (4608791)](https://en.wikipedia.org/wiki/Sago_Mine_disaster)

@@

#### [Crandall Canyon Mine (4201715)](https://www.google.com/url?sa=t&rct=j&q=&esrc=s&source=web&cd=2&cad=rja&uact=8&ved=0ahUKEwjOyeGnvtTSAhVN42MKHdtyD7UQFggnMAE&url=http%3A%2F%2Fwww.deseretnews.com%2Farticle%2F695206530%2FVictims-of-Crandall-Canyon-Mine-disaster.html&usg=AFQjCNHqcZNs-qEa9SipaDkfKfYy5okkGQ&sig2=WMuhLw2C0D1jAxkiBM1uiw)

```{r crandall, echo=FALSE}
library(ggplot2)
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}

yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4201715 & year < 2007) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = "line",
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```
